Describing vocalizations in young children: A big data approach through citizen science annotation

### 2021-01-28 202010_jslhr/paper.Rmd
cleaned up pipeline in progress

printr=function(x) sub("0.", ".", round(x,3))
```

```{r read-in}
# read datasets

data_ang <- read.csv("segment_AS.csv",header=T,sep =",")
data_td <- read.csv("segment_LRC.csv")
data_all<-rbind(data_ang, data_td)

>>>>

printr=function(x) sub("0.", ".", round(x,3))

#document session info

sink("lastknit_session_info.txt")
sessionInfo()
sink()
```

```{r read-in}
x <- read.csv("../data_analyses/output/metadata_all_PU.csv",header=T,sep =",")
y <- read.csv("../data_analyses/files_from_zooniverse/zooniverse_data_all_final.csv",header=T,sep =",")
x$AudioData=paste0(x$AudioData,".mp3")
merge(x,y,by="AudioData")->chunks

chunks$chunkID=paste(chunks$ChildID,chunks$onset)

#merge with children's info
demo_data <- read.csv("../data_analyses/files_from_elsewhere/demo-data.tsv",header=T,sep ="\t")
merge(demo_data,chunks,by="ChildID")->chunks

write.csv(chunks,"../data_analyses/output/chunks_individual_judgments.csv")

# next version collapses across chunks to get the nb of different classifications
table(chunks$chunkID,chunks$Answer)->mytab
mytab_mj <- mytab>=3  #set as True the answer types that have 3 or more votes
mymj <- t(t(apply(mytab_mj, 1, function(u) paste( names(which(u)), collapse=", " )))) #get the answer that has majority vote
nvotes<- t(t(apply(mytab, 1, max))) #get the number of votes for that 
maj_jud=cbind(row.names(mytab),mymj,nvotes)
colnames(maj_jud)<-c("chunkID","Answer","nvotes")
maj_jud2=as.data.frame(maj_jud)
maj_jud2$ChildID = gsub(" .*","",maj_jud2$chunkID)

#add participant information
merge(demo_data,maj_jud2,by="ChildID")->maj_jud

write.csv(maj_jud,"../data_analyses/output/chunks_maj_judgments.csv")

#add segment-level info from the lab
#TODO !!!

# read datasets
data_ang <- read.csv("segment_AS.csv",header=T,sep =",")
data_td <- read.csv("segment_LRC.csv")
data_all<-rbind(data_ang, data_td)
